HPC Final Project

### 2019-05-26 report/draft.tex
Update the tex

\paragraph{Reformulation by Gaussian Gridding \& FFT} 
The basic idea is convolution by the Gaussian... leave it for later.

>>>>

\paragraph{Reformulation by Gaussian Gridding \& FFT} 
The basic idea of conducting NuFFT here is to consider the point source as delta function and convolve it with Gaussian function to smooth it in the real space, which makes it possible to the uniform FFT. Then we conduct deconvolution in the frequency space by scaling (element-wise multiplication) and get the finally result. We will give more details in this section.
